CorReg pretreatment : Regression for correlated variables and application in steel industry

### 2014-03-14 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@450 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@451 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator &OLS  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 81781.54 (247281.7) & 507.1 (269.2) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25.06 (0.2) \\
 &  &HU &MSE (sd) & 81781.54 (247281.7) & 587.07 (425.6) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25.06 (0.2) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 74136.81 (297716.1) & 189.45 (48.1) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 13.85 (0.9) & 9.27 (0.5) \\
 &  & HU & MSE (sd) & 74136.81 (297716.1) & 340.53 (169.4) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 21 (0) & 9.27 (0.5) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 684.04 (438.1) & 190.97 (37.7) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.43 (0.7) & 25.13 (0.4) \\
 &  &HU &MSE (sd) & 684.04 (438.1) & 196.36 (40.5) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.99 (0.5) & 25.13 (0.4) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 596.32 (323) & 126.94 (15.5) & 119.39 (12.4) \\
& & & cpl (sd) & 41 (0) & 11.45 (0.9) & 9.13 (0.3) \\
 &  &HU &MSE (sd) & 596.32 (323) & 168.03 (27.7) & 119.39 (12.4) \\
& & &cpl (sd) & 41 (0) & 21 (0) & 9.13 (0.3) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U&  MSE (sd) & 168.35 (20.1) & 133.75 (12.4) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 24.53 (0.7) & 25.08 (0.3) \\
 &  &HU &  MSE (sd) & 168.35 (20.1) & 135.04 (13.1) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 25.01 (0.4) & 25.08 (0.3) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  MSE (sd) & 168.07 (21.4) & 109.61 (7.4) & 108.64 (7.2) \\
& & &  cpl (sd) & 41 (0) & 10.02 (0.8) & 9.25 (0.5) \\
 &  &HU & MSE (sd) & 168.07 (21.4) & 124.23 (11.1) & 108.64 (7.2) \\
& & & cpl (sd) & 41 (0) & 21 (0) & 9.25 (0.5) \\
\hline
\end{tabular} 
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X2$. } \label{YX2linOLS}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator &LAR  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 367.45 (198.4) & 298.32 (122.4) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.9 (3.8) & 12.84 (3.8) \\
 &  &HU &MSE (sd) & 367.45 (198.4) & 298.1 (119.1) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.81 (3.8) & 12.84 (3.8) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 273.12 (267.2) & 166.93 (49) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 8.7 (2.5) & 7.45 (1.4) \\
 &  & HU & MSE (sd) & 273.12 (267.2) & 175.68 (57.5) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 9.19 (2.9) & 7.45 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 189.64 (52.5) & 171.97 (45.9) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.4 (2.8) & 13.5 (3.1) \\
 &  &HU &MSE (sd) & 189.64 (52.5) & 174.36 (45.3) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.57 (3) & 13.5 (3.1) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 163.88 (67.4) & 124.53 (17) & 121.99 (16.6) \\
& & & cpl (sd) & 13.06 (7.2) & 8.29 (1.6) & 7.73 (1.2) \\
 &  &HU &MSE (sd) & 163.88 (67.4) & 133.7 (26.4) & 121.99 (16.6) \\
& & &cpl (sd) & 13.06 (7.2) & 9.65 (3.3) & 7.73 (1.2) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U& MSE (sd) & 129.65 (14.8) & 127.11 (12.1) & 127.46 (12.2) \\
& & &  cpl (sd) & 14.86 (3.1) & 13.97 (2.5) & 14.04 (2.5) \\
 &  &HU &  MSE (sd) & 129.65 (14.8) & 127.46 (12.2) & 127.46 (12.2) \\
& & & cpl (sd) & 14.86 (3.1) & 14.02 (2.5) & 14.04 (2.5) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  MSE (sd) & 121.21 (20.1) & 109.66 (7.9) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 8.42 (1.1) & 8.11 (0.8) \\
 &  &HU &  MSE (sd) & 121.21 (20.1) & 112.56 (11.2) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 9.77 (2.3) & 8.11 (0.8) \\
\hline
\end{tabular} 
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X2$. }\label{YX2linLASSO}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator & Elasticnet  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 499.32 (218.8) & 311.41 (137.4) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.75 (4.8) & 11.49 (4.7) \\
 &  &HU &MSE (sd) & 499.32 (218.8) & 307.6 (128.7) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.63 (4.7) & 11.49 (4.7) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 691.55 (503.2) & 193.45 (54.2) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 10.26 (2.7) & 7.81 (1.4) \\
 &  & HU & MSE (sd) & 691.55 (503.2) & 279.21 (117.3) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 13 (4.3) & 7.81 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 282.05 (134.8) & 180.64 (47.6) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 13.68 (4) & 14.05 (4) \\
 &  &HU &MSE (sd) & 282.05 (134.8) & 180.84 (47.5) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 14.03 (4) & 14.05 (4) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 308.13 (142.9) & 129.39 (19.6) & 122.71 (17.8) \\
& & & cpl (sd) & 22.94 (7.7) & 9.37 (2.1) & 7.91 (1.4) \\
 &  &HU &MSE (sd) & 308.13 (142.9) & 159.14 (30.4) & 122.71 (17.8) \\
& & &cpl (sd) & 22.94 (7.7) & 15.42 (4) & 7.91 (1.4) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U& MSE (sd) & 150.14 (19.7) & 127.48 (14) & 128.21 (15) \\
& & &  cpl (sd) & 25.6 (5.4) & 14.73 (3.8) & 14.73 (3.9) \\
 &  &HU &  MSE (sd) & 150.14 (19.7) & 128.21 (14.9) & 128.21 (15) \\
& & & cpl (sd) & 25.6 (5.4) & 14.7 (3.9) & 14.73 (3.9) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U& MSE (sd) & 157.18 (23.5) & 110.24 (8) & 109.24 (7.8) \\
& & &  cpl (sd) & 30.41 (6.7) & 8.96 (1.3) & 8.3 (1) \\
 &  &HU &  MSE (sd) & 157.18 (23.5) & 123.8 (12.5) & 109.24 (7.8) \\
& & & cpl (sd) & 30.41 (6.7) & 17.18 (3.3) & 8.3 (1) \\
\hline
\end{tabular} 
\caption{Elasticnet (with Elasticnet) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X2$.}\label{YX2linenet}
\end{table}

>>>>

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator &OLS  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 81781.54 (247281.7) & 507.1 (269.2) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25.06 (0.2) \\
 &  &HU &MSE (sd) & 81781.54 (247281.7) & 587.07 (425.6) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25.06 (0.2) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 74136.81 (297716.1) & 189.45 (48.1) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 13.85 (0.9) & 9.27 (0.5) \\
 &  & HU & MSE (sd) & 74136.81 (297716.1) & 340.53 (169.4) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 21 (0) & 9.27 (0.5) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 684.04 (438.1) & 190.97 (37.7) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.43 (0.7) & 25.13 (0.4) \\
 &  &HU &MSE (sd) & 684.04 (438.1) & 196.36 (40.5) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.99 (0.5) & 25.13 (0.4) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 596.32 (323) & 126.94 (15.5) & 119.39 (12.4) \\
& & & cpl (sd) & 41 (0) & 11.45 (0.9) & 9.13 (0.3) \\
 &  &HU &MSE (sd) & 596.32 (323) & 168.03 (27.7) & 119.39 (12.4) \\
& & &cpl (sd) & 41 (0) & 21 (0) & 9.13 (0.3) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U&  MSE (sd) & 168.35 (20.1) & 133.75 (12.4) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 24.53 (0.7) & 25.08 (0.3) \\
 &  &HU &  MSE (sd) & 168.35 (20.1) & 135.04 (13.1) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 25.01 (0.4) & 25.08 (0.3) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  MSE (sd) & 168.07 (21.4) & 109.61 (7.4) & 108.64 (7.2) \\
& & &  cpl (sd) & 41 (0) & 10.02 (0.8) & 9.25 (0.5) \\
 &  &HU & MSE (sd) & 168.07 (21.4) & 124.23 (11.1) & 108.64 (7.2) \\
& & & cpl (sd) & 41 (0) & 21 (0) & 9.25 (0.5) \\
\hline
\end{tabular} 
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X_2$. } \label{YX2linOLS}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator &LAR  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 367.45 (198.4) & 298.32 (122.4) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.9 (3.8) & 12.84 (3.8) \\
 &  &HU &MSE (sd) & 367.45 (198.4) & 298.1 (119.1) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.81 (3.8) & 12.84 (3.8) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 273.12 (267.2) & 166.93 (49) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 8.7 (2.5) & 7.45 (1.4) \\
 &  & HU & MSE (sd) & 273.12 (267.2) & 175.68 (57.5) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 9.19 (2.9) & 7.45 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 189.64 (52.5) & 171.97 (45.9) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.4 (2.8) & 13.5 (3.1) \\
 &  &HU &MSE (sd) & 189.64 (52.5) & 174.36 (45.3) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.57 (3) & 13.5 (3.1) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 163.88 (67.4) & 124.53 (17) & 121.99 (16.6) \\
& & & cpl (sd) & 13.06 (7.2) & 8.29 (1.6) & 7.73 (1.2) \\
 &  &HU &MSE (sd) & 163.88 (67.4) & 133.7 (26.4) & 121.99 (16.6) \\
& & &cpl (sd) & 13.06 (7.2) & 9.65 (3.3) & 7.73 (1.2) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U& MSE (sd) & 129.65 (14.8) & 127.11 (12.1) & 127.46 (12.2) \\
& & &  cpl (sd) & 14.86 (3.1) & 13.97 (2.5) & 14.04 (2.5) \\
 &  &HU &  MSE (sd) & 129.65 (14.8) & 127.46 (12.2) & 127.46 (12.2) \\
& & & cpl (sd) & 14.86 (3.1) & 14.02 (2.5) & 14.04 (2.5) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  MSE (sd) & 121.21 (20.1) & 109.66 (7.9) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 8.42 (1.1) & 8.11 (0.8) \\
 &  &HU &  MSE (sd) & 121.21 (20.1) & 112.56 (11.2) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 9.77 (2.3) & 8.11 (0.8) \\
\hline
\end{tabular} 
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X_2$. }\label{YX2linLASSO}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator & Elasticnet  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 499.32 (218.8) & 311.41 (137.4) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.75 (4.8) & 11.49 (4.7) \\
 &  &HU &MSE (sd) & 499.32 (218.8) & 307.6 (128.7) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.63 (4.7) & 11.49 (4.7) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 691.55 (503.2) & 193.45 (54.2) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 10.26 (2.7) & 7.81 (1.4) \\
 &  & HU & MSE (sd) & 691.55 (503.2) & 279.21 (117.3) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 13 (4.3) & 7.81 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 282.05 (134.8) & 180.64 (47.6) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 13.68 (4) & 14.05 (4) \\
 &  &HU &MSE (sd) & 282.05 (134.8) & 180.84 (47.5) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 14.03 (4) & 14.05 (4) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 308.13 (142.9) & 129.39 (19.6) & 122.71 (17.8) \\
& & & cpl (sd) & 22.94 (7.7) & 9.37 (2.1) & 7.91 (1.4) \\
 &  &HU &MSE (sd) & 308.13 (142.9) & 159.14 (30.4) & 122.71 (17.8) \\
& & &cpl (sd) & 22.94 (7.7) & 15.42 (4) & 7.91 (1.4) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U& MSE (sd) & 150.14 (19.7) & 127.48 (14) & 128.21 (15) \\
& & &  cpl (sd) & 25.6 (5.4) & 14.73 (3.8) & 14.73 (3.9) \\
 &  &HU &  MSE (sd) & 150.14 (19.7) & 128.21 (14.9) & 128.21 (15) \\
& & & cpl (sd) & 25.6 (5.4) & 14.7 (3.9) & 14.73 (3.9) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U& MSE (sd) & 157.18 (23.5) & 110.24 (8) & 109.24 (7.8) \\
& & &  cpl (sd) & 30.41 (6.7) & 8.96 (1.3) & 8.3 (1) \\
 &  &HU &  MSE (sd) & 157.18 (23.5) & 123.8 (12.5) & 109.24 (7.8) \\
& & & cpl (sd) & 30.41 (6.7) & 17.18 (3.3) & 8.3 (1) \\
\hline
\end{tabular} 
\caption{Elasticnet (with Elasticnet) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X_2$.}\label{YX2linenet}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator &Stepwise  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 394.59 (454.6) & 341.47 (153.2) & 351.14 (148) \\
& & & cpl (sd) & 13.09 (3.2) & 12.9 (2.9) & 12.92 (3) \\
 &  &HU &MSE (sd) & 394.59 (454.6) & 353.99 (157) & 351.14 (148) \\
& & & cpl (sd) & 13.09 (3.2) & 12.83 (2.9) & 12.92 (3) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 410.11 (343.5) & 163.05 (45.4) & 152.08 (38.1) \\
& & & cpl (sd) & 15.8 (6.5) & 8.29 (2.2) & 7.34 (1.3) \\
 &  & HU & MSE (sd) & 410.11 (343.5) & 178.94 (69.7) & 152.08 (38.1) \\
& & & cpl (sd) & 15.8 (6.5) & 8.89 (3) & 7.34 (1.3) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 180.67 (52.7) & 173.02 (38.3) & 174.84 (36.8) \\
& & & cpl (sd) & 13.56 (3.7) & 12.78 (2.4) & 13.07 (2.4) \\
 &  &HU &MSE (sd) & 180.67 (52.7) & 175.3 (38.1) & 174.84 (36.8) \\
& & & cpl (sd) & 13.56 (3.7) & 13.01 (2.4) & 13.07 (2.4) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 188.91 (88.5) & 124.38 (17.4) & 122.38 (16.7) \\
& & & cpl (sd) & 14.74 (6.6) & 8.07 (1.6) & 7.65 (1.2) \\
 &  &HU &MSE (sd) & 188.91 (88.5) & 134.22 (23.6) & 122.38 (16.7) \\
& & &cpl (sd) & 14.74 (6.6) & 9.5 (2.8) & 7.65 (1.2) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U&  MSE (sd) & 128.18 (13.7) & 127.43 (13.7) & 127.71 (13.3) \\
& & &  cpl (sd) & 13.78 (2.8) & 13.51 (2) & 13.59 (2.1) \\
 &  &HU & MSE (sd) & 128.18 (13.7) & 127.71 (13.3) & 127.71 (13.3) \\
& & & cpl (sd) & 13.78 (2.8) & 13.59 (2.1) & 13.59 (2.1) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U& MSE (sd) & 126.15 (20.6) & 109.47 (8) & 109.04 (7.8) \\
& & & cpl (sd) & 13.25 (4.4) & 8.3 (1) & 8.12 (0.8) \\
 &  &HU &  MSE (sd) & 126.15 (20.6) & 113.96 (11.4) & 109.04 (7.8) \\
& & & cpl (sd) & 13.25 (4.4) & 10.08 (2.6) & 8.12 (0.8) \\
\hline
\end{tabular} 
\caption{Stepwise  combined with constrained \textsc{CorReg}. $Y$ depends on all variables in $X_2$.}\label{YX2linstep}
\end{table}
